DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-07 paper/intro.tex
Small edits to intro

% broad context:
% - advance in ai sparked interests in the robotics application, such as
%   self-driving cars.
% - in particular, deep neural network models are increasingly used
%   for perception and control of a vehicle. say. AI workloads.
%
%
Autonomous cars have been a topic of increasing interest in recent
years as many companies are actively developing related hardware
and software technologies toward fully autonomous driving capability without
any human intervention. Deep neural networks (DNNs) have been
successfully applied in various perception and control tasks in
recent years, and they are important workloads for autonomous vehicles
as well. For example, Tesla Model S was known to use a specialized
chip (MobileEye EyeQ), which uses a deep neural network for vision-based
real-time obstacle detection and avoidance. More recently, researchers
are investigating DNN based end-to-end control of
cars~\cite{Bojarski2016} and other robots. It is expected that more
DNN based Artificial Intelligence workloads may be used in future
autonomous vehicles.

% big problem
Executing these AI workloads on an embedded computing platform that can
be used in a car poses several additional challenges. First, many AI
workloads in vehicles are computationally demanding and have strict
real-time requirements. For example, latency in a vision-based object
detection task may be directly linked to safety of the vehicle. This
requires a high computing capacity as well as means to guaranteeing
the timings. On the other hand, the computing hardware platform must
also satisfy cost, size, weight, and power constraints, which require
highly efficient computing platform. These two conflicting
requirements  complicate the platform selection process as observed in
~\cite{Otterness2017}, which evaluated vision workloads on
NVIDIA's Tegra TX1 platform.

@@

% related work and remaining problems
To understand what kind of computing hardware is needed for AI
workloads, we need a testbed and realistic workloads. While a real car
testbed would be most ideal, it is not only highly expensive but also
poses serious safety concerns that hinder development and exploration.
Therefore, there is a strong need for safer and less costly testbeds
that still employ state-of-the-art AI technologies. There are already
several relatively inexpensive RC-car based testbeds, such as MIT
RaceCar~\cite{shin2017project} and UPenn's F1$/$10 racecar~\cite{upennf1tenth}.
However, these RC-car testbeds still cost more than \$3,000.

@@

% contributions
The {\bf contributions} of this paper are as follows:
\begin{itemize}
  \item We present the design and implementation of a
    low-cost autonomous vehicle testbed DeepPicar, which utilizes the
    state-of-the-art artificial intelligence techniques.
  \item We provide an analysis and case-study of real-time issues in the
    DeepPicar.
  \item We systematically compare real-time computing capabilities of
    multiple embedded computing platforms in the context of a
    vision-based autonomous driving.
\end{itemize}

@@

The remaining sections of the paper are as follows: Section II 
provides a background of applications in autonomous driving. Section 
III gives an overview of the DeepPicar platform, including the 
high-level system and the methods used for training and inference. 
Section IV presents our evaluation of the platform and how different 
factors can affect performance. Section V gives a comparison between 
the Raspberry Pi 3 and other embedded computing platforms to 
determine their suitably for autonomous driving research. Related 
works are discussed in Section VI, and the paper finishes with 
conclusions in Section VII.

>>>>

% broad context:
% - advance in ai sparked interests in the robotics application, such as
%   self-driving cars.
% - in particular, deep neural network models are increasingly used
%   for perception and control of a vehicle. say. AI workloads.
%
%
Autonomous cars have been a topic of increasing interest in recent
years as many companies are actively developing related hardware
and software technologies toward fully autonomous driving capability with
no human intervention. Deep neural networks (DNNs) have been
successfully applied in various perception and control tasks in
recent years.  They are important workloads for autonomous vehicles
as well. For example, Tesla Model S was known to use a specialized
chip (MobileEye EyeQ), which uses a deep neural network for vision-based
real-time obstacle detection and avoidance. More recently, researchers
are investigating DNN based end-to-end control of
cars~\cite{Bojarski2016} and other robots. It is expected that more
DNN based Artificial Intelligence workloads may be used in future
autonomous vehicles.

% big problem
Executing these AI workloads on an embedded computing platform that can
be used in a car poses several additional challenges. First, many AI
workloads in vehicles are computationally demanding and have strict
real-time requirements. For example, latency in a vision-based object
detection task may be directly linked to safety of the vehicle. This
requires a high computing capacity as well as the means to guaranteeing
the timings. On the other hand, the computing hardware platform must
also satisfy cost, size, weight, and power constraints, which require
highly efficient computing platform. These two conflicting
requirements  complicate the platform selection process as observed in
~\cite{Otterness2017}, which evaluated vision workloads on
NVIDIA's Tegra TX1 platform.

@@

% related work and remaining problems
To understand what kind of computing hardware is needed for AI
workloads, we need a testbed and realistic workloads. While using a real car
based testbed would be most ideal, it is not only highly expensive but also
poses serious safety concerns that hinder development and exploration.
Therefore, there is a strong need for safer and less costly testbeds
that still employ state-of-the-art AI technologies. There are already
several relatively inexpensive RC-car based testbeds, such as MIT
RaceCar~\cite{shin2017project} and UPenn's F1$/$10 racecar~\cite{upennf1tenth}.
However, these RC-car testbeds still cost more than \$3,000.

@@

% contributions
The {\bf contributions} of this paper are as follows:
\begin{itemize}
  \item We present the design and implementation of a
    low-cost autonomous vehicle testbed DeepPicar, which utilizes the
    state-of-the-art artificial intelligence techniques.
  \item We provide an analysis and case-study of real-time issues in the
    DeepPicar.
  \item We systematically compare real-time computing capabilities of
    multiple embedded computing platforms in the context of
    vision-based autonomous driving.
\end{itemize}

@@

The remaining sections of the paper are as follows: Section II 
provides a background of applications in autonomous driving and related works.
 Section III gives an overview of the DeepPicar platform, including the 
high-level system and the methods used for training and inference. 
Section IV presents our evaluation of the platform and how different 
factors can affect performance. Section V gives a comparison between 
the Raspberry Pi 3 and other embedded computing platforms to 
determine their suitably for autonomous driving research. The paper finishes with 
conclusions in Section VI.
